---
output: github_document
---
```{r, echo = FALSE}

description <- read.dcf('DESCRIPTION')
version <- as.vector(description[, 'Version'])
rvers = stringr::str_extract(pattern = "\\d+\\.\\d\\.\\d+", string =  as.vector(description[,"Depends"]))
```
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)[![license](https://img.shields.io/github/license/mashape/apistatus.svg)](https://choosealicense.com/licenses/mit/)[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r rvers`-6666ff.svg)](https://cran.r-project.org/)[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)

<!-- badges: start -->
  [![R-CMD-check](https://github.com/GuanLab/DDR-drug-synergy-prediction-ShinyApp/workflows/R-CMD-check/badge.svg)](https://github.com/GuanLab/DDR-drug-synergy-prediction-ShinyApp/actions)
  <!-- badges: end -->

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# guanlabddrdrugcombination

Welcome to our shiny app for DDR drug synergy and efficacy prediction repository.
This repository implements a shiny app that provides a general overview of all
features used for the predictions, the predictions on out 67 cell lines and summary
plots for SHAP analysis on out data. Additionally, you can upload molecular data
and analyse predicted synergy and efficacy scores of our model

## Requirements

* R 4.1.1
* git2r
* renv

## Installation

To run the app, you will need to install the devtools, git2r and renv package.
The following code will clone and restore the R package versions that were
tested by us.

```{R, eval=FALSE}
install.packages(c('renv', 'git2r'))

# Clone repository
git2r::clone("https://github.com/GuanLab/DDR-drug-synergy-prediction-ShinyApp.git", 
             branch = "renv_support", local_path="guanlabddrdrugcombination")

# Initialize and restore packages using renv
renv::activate(project = "guanlabddrdrugcombination")
renv::restore(project = "guanlabddrdrugcombination", prompt = FALSE)

shiny::runApp('guanlabddrdrugcombination/inst/app/')
```

After a restart of your R session, you can start the app using:

```{R, eval=FALSE}
library(guanlabddrdrugcombination)

launch_synergy_ddr_app()
```
