---
output: github_document
---
```{r, echo = FALSE}

description <- read.dcf('DESCRIPTION')
version <- as.vector(description[, 'Version'])
rvers = stringr::str_extract(pattern = "\\d+\\.\\d\\.\\d+", string =  as.vector(description[,"Depends"]))
```
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)[![license](https://img.shields.io/github/license/mashape/apistatus.svg)](https://choosealicense.com/licenses/mit/)[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r rvers`-6666ff.svg)](https://cran.r-project.org/)[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)

<!-- badges: start -->
  [![R-CMD-check](https://github.com/GuanLab/DDR-drug-synergy-prediction-ShinyApp/workflows/R-CMD-check/badge.svg)](https://github.com/GuanLab/DDR-drug-synergy-prediction-ShinyApp/actions)
  <!-- badges: end -->

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# guanlabddrdrugcombination

Welcome to our shiny app for DDR drug synergy and efficacy prediction repository.
This repository implements a shiny app that provides a general overview of all
features used for the predictions, the predictions on out 67 cell lines and summary
plots for SHAP analysis on out data. Additionally, you can upload molecular data
and analyse predicted synergy and efficacy scores of our model

## Requirements

This application was tested using R 4.1.1.


## Installation

To run the app, you will need to install the devtools package.

```{R, eval=FALSE}
install.packages('devtools')
```

Next you can install the app using:

```{R, eval=FALSE}
devtools::install_github("GuanLab/DDR-drug-synergy-prediction-ShinyApp")
```

After a restart of your R session, you can start the app using:

```{R, eval=FALSE}
library(guanlabddrdrugcombination)

launch_synergy_ddr_app()
```
